Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization

### 2023-05-13 manuscript.Rmd
update to apa7

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
shorttitle: "The Objective of Preregistration"
author: 
  - name: Aaron Peikert
    affiliation: "1,2,3"
    email: peikert@mpib-berlin.mpg.de
    corresponding : yes    # Define only one corresponding author
    address: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
  - name: Andreas M. Brandmaier
    affiliation: "1, 2, 4"
affiliation:
  - id: 1
    institution: Max Planck Institute for Human Development
  - id: 2
    institution: Max Planck UCL Centre for Computational Psychiatry and Ageing Research
  - id: 3
    institution: Humboldt-Universität zu Berlin
  - id: 4
    institution: MSB Medical School Berlin
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; Bayesian; Open Science
wordcount         : "`r tryCatch(wordcountaddin::word_count(), error = function(x)'~7000')`"
figsintext: false
figurelist: false
tablelist : false
footnotelist: false
lineno: true
linkcolor: "blue"
csquotes: false
class: "man"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
header-includes:
  - \raggedbottom
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
    - crsh/papaja@1c488f7
  tlmgr:
    - apa6
    - pgf
    - preview
  apt:
    - git
    - rsync
    - curl
    - inkscape
note: |
  The materials for this article are available on [GitHub](https://github.com/aaronpeikert/bayes-prereg) [@zenodo-release].
  This version was created from git commit ``r repro::current_hash(backend = "gert")``.
  The manuscript is available as [preprint](https://www.doi.org/10.31234/osf.io/cs8wb) [@peikertWhyDoesPreregistration2023] and was submitted to [Psychological Methods](https://www.apa.org/pubs/journals/).

>>>>

---
title: "Why does preregistration increase the persuasiveness of evidence? A Bayesian rationalization"
bibliography: references.bib
abstract: "`r paste0(c('\\\\noindent', readLines('abstract.md')), collapse = ' ')`"
shorttitle: "The Objective of Preregistration"
author: 
  - name: Aaron Peikert
    affiliation: "1,2,3"
    email: peikert@mpib-berlin.mpg.de
    corresponding : yes    # Define only one corresponding author
    address: "Center for Lifespan Psychology, Max Planck Institute for Human Development, Lentzeallee 94, 14195 Berlin, Germany"
  - name: Andreas M. Brandmaier
    affiliation: "1, 2, 4"
affiliation:
  - id: 1
    institution: Max Planck Institute for Human Development
  - id: 2
    institution: Max Planck UCL Centre for Computational Psychiatry and Ageing Research
  - id: 3
    institution: Humboldt-Universität zu Berlin
  - id: 4
    institution: MSB Medical School Berlin
keywords: |
  preregistration; confirmation; exploration; hypothesis testing; Bayesian; Open Science
wordcount         : "`r tryCatch(wordcountaddin::word_count(), error = function(x)'~7000')`"
figsintext: false
figurelist: false
tablelist : false
footnotelist: false
lineno: true
linkcolor: "blue"
csquotes: false
class: "man"
documentclass: "apa7"
csl: "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
header-includes: |
  \raggedbottom
  \makeatletter

  \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
    {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
    {-1em}%
    {\normalfont\normalsize\bfseries\typesectitle}}
  \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
    {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
    {-\z@\relax}%
    {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
  \makeatother
repro:
  scripts:
    - R/plots.R
  files:
    - abstract.md
    - data/simulation.rds
  packages:
    - here
    - tidyverse
    - ggplot2
    - ggthemes
    - patchwork
    - tikzDevice
    - rticles
    - gert
    - aaronpeikert/repro@5075336
    - crsh/papaja@1c488f7
  tlmgr:
    - apa7
    - pgf
    - preview
  apt:
    - git
    - rsync
    - curl
    - inkscape
note: |
  The materials for this article are available on [GitHub](https://github.com/aaronpeikert/bayes-prereg) [@zenodo-release].
  This version was created from git commit ``r repro::current_hash(backend = "gert")``.
  The manuscript is available as [preprint](https://www.doi.org/10.31234/osf.io/cs8wb) [@peikertWhyDoesPreregistration2023] and was submitted to [Psychological Methods](https://www.apa.org/pubs/journals/).
